---
title: "week 14"
author: "sophia"
date: "2024-05-21"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth: false
---

```{r}
library(knitr)
knitr::opts_chunk$set(echo = T)
```

# AI Prompt

## Preset

You are an assistant to data visualization. You use R in tidyverse style for assistance. If you are asked for scripts, your answer is only in R scripts with concise comments -- no other non-script explanation is required. The first line of your code chunk must be a comment line. Its format is `# {{summary_title}} -----` where `{{summary_title}}` is your short summary of the assisted task. Other R script rules are: whenever there is a need to show result, if the result is a data frame, slice its first 3 rows and use `glimpse`; otherwise, use `head` instead of `print`.

For plotting, always use `theme_minimal` when it is not a map. If it uses map, use `theme_void` instead. Except `theme_void`, the x-axis line should be a solid black. If creating a new plot, always create a plot object and show it. If adding layers to an existing plot, always show the plot after adding each layer. A plot should always have a title, and a subtitle to show the unit of y axis. In addition, there should be a footnote showing data source.

For map data, always use `geom_sf` for plotting unless impossible. When simplifying simple features, always use `st_simplify` with `preserveTopology = TRUE` and `dTolerance =1`.

When requesting data from OpenStreetMap, always use `osmdata` package. When requesting data from OpenStreetMap, always use `osmdata` package. When construct a query, always use `osmdata::opq` with `timeout=60` and `osmdata::add_osm_feature`.

When asking ploting regarding Taiwan, always add text information telling user that they can also use `mp <- econDV2::Map(); mp$sf$get_sf_taiwan_simplified() -> taiwan` to get `taiwan` which is a list containing common Taiwan administration boundaries simple features.

The first code you give should always `library(tidyverse)`. The first code that involves with simple feature should always `library(sf)`.

If you understand your role, say it -- no need to show any code at this time.

## Tasks Prompt

Here is a data frame 'companies' like this: \$ year <int> 2000, 2002, 2004, 2006, 2008, 2010, 2012, 2014, 2016, 2018, 2020,… \$ company <chr> "Microsoft", "Microsoft", "Microsoft", "Microsoft", "Microsoft", … \$ market_cap <dbl> 5.100400e+11, 2.838210e+11, 2.954774e+11, 2.937800e+11, 1.801852e… Code a line chart following material design UI.

# Trillion-dollar tech company market cap

```{r}
# Trillion-dollar tech company market cap -----
library(tidyverse)
library(sf)

# Data frame 'companies'
companies <- tribble(
  ~year, ~company, ~market_cap,
  2000, "Microsoft", 510040000000,
  2002, "Microsoft", 283821040000,
  2004, "Microsoft", 295477440000,
  2006, "Microsoft", 293780000000,
  2008, "Microsoft", 180185200000,
  2010, "Microsoft", 219134720000,
  2012, "Microsoft", 249272320000,
  2014, "Microsoft", 355376000000,
  2016, "Microsoft", 482198400000,
  2018, "Microsoft", 859371520000,
  2020, "Microsoft", 1631568000000,
  2000, "Amazon", 16545600000,
  2002, "Amazon", 6679200000,
  2004, "Amazon", 17517600000,
  2006, "Amazon", 19166400000,
  2008, "Amazon", 31764800000,
  2010, "Amazon", 74334400000,
  2012, "Amazon", 115655200000,
  2014, "Amazon", 150788800000,
  2016, "Amazon", 356789600000,
  2018, "Amazon", 737632000000,
  2020, "Amazon", 1592000000000,
  2004, "Alphabet", 51151200000,
  2006, "Alphabet", 117914400000,
  2008, "Alphabet", 115070400000,
  2010, "Alphabet", 193416000000,
  2012, "Alphabet", 249995200000,
  2014, "Alphabet", 345599200000,
  2016, "Alphabet", 546762400000,
  2018, "Alphabet", 766757600000,
  2020, "Alphabet", 1190000000000,
  2012, "Facebook", 63804800000,
  2014, "Facebook", 213555200000,
  2016, "Facebook", 368966400000,
  2018, "Facebook", 424764800000,
  2020, "Facebook", 792000000000,
  2012, "Apple", 556624000000,
  2014, "Apple", 642630400000,
  2016, "Apple", 586038400000,
  2018, "Apple", 851358400000,
  2020, "Apple", 2312120000000
)

companies %>%
  mutate(year = as.integer(year)) %>%
  glimpse()

# Plotting the line chart
line_chart <- ggplot(companies, aes(x = year, y = market_cap, color = company)) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 3) +
  labs(
    title = "Market Capitalization Over Years",
    subtitle = "Market Cap in USD",
    x = "Year",
    y = "Market Capitalization",
    caption = "Source: Company Data"
  ) +
  theme_minimal() +
  theme(
    axis.line.x = element_line(color = "black"),
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 10),
    plot.caption = element_text(size = 8, hjust = 0)
  )

line_chart

```

# Practice at home

## AI Prompt

此筆資料已經透過以下程式碼匯入：

```         
library(readr)
Legislative_Yuan_Movement <- read_csv("~/Downloads/Legislative Yuan Movement-codebook.csv")
```

請把`z6`和`z6_o5`變項重新編碼成新變項`area`加入`Legislative_Yuan_Movement`中，編碼規則如下：

在`z6`變項中，1="濟南路" 2="青島東路大門東側（往林森南路方向）" 3="立法院庭院內" 4="青島東路大門西側 （往中山南路方向）" 5="其他（請說明"，依照1=1 "濟南路" 2 4 =2 "青島東路" 5=5"其他"，重新編碼成`area`變項。

`area`變項依據`z6_o5`變項中， 如果是"靠外交部"、"外交部側"或"群賢樓前"，`area`變項重新編碼成1="濟南路" 如果是"A"、"A右"、"A2"、"A右2"、"A右大帳篷"、"A2右"、"青島舞臺最裡最右"或"青舞臺前"，`area`變項重新編碼成2="青島東路"； 如果是"中山南路上"或"中山南路"，`area`變項重新編碼成3="中山南路"； 如果是"教會"、"濟南教會"、"濟南教堂"或"濟南教會區"，`area`變項重新編碼成4="濟南教會"。

## Import data

```{r}
library(readr)
Legislative_Yuan_Movement <- read_csv("~/Downloads/Legislative Yuan Movement-codebook.csv")

```

## Recode z6 variable

```{r}
library(tidyverse)

Legislative_Yuan_Movement <- Legislative_Yuan_Movement %>%
  mutate(area = case_when(
    z6 == 1 ~ 1,
    z6 %in% c(2, 4) ~ 2,
    z6 == 5 ~ 5
  ))

```

## Recode area variable based on z6_o5

```{r}
Legislative_Yuan_Movement <- Legislative_Yuan_Movement %>%
  mutate(area = case_when(
    z6_o5 %in% c("靠外交部", "外交部側", "群賢樓前") ~ 1,
    z6_o5 %in% c("A", "A右", "A2", "A右2", "A右大帳篷", "A2右", "青島舞臺最裡最右", "青舞臺前") ~ 2,
    z6_o5 %in% c("中山南路上", "中山南路") ~ 3,
    z6_o5 %in% c("教會", "濟南教會", "濟南教堂", "濟南教會區") ~ 4,
    TRUE ~ area
  ))
```

## Plot

```{r}
# Visualize area distribution with sample counts using circle size and color -----
library(tidyverse)
library(sf)
library(osmdata)
library(econDV2)

# Define bounding boxes for each area
bbox_list <- list(
  jinan_rd = c(121.51812, 25.04448, 121.52357, 25.04123),
  qingdao_rd = c(121.51898, 25.04508, 121.52170, 25.04346),
  zhongshan_rd = c(121.51786, 25.04470, 121.52058, 25.04308),
  jinan_church = c(121.51814, 25.04427, 121.52086, 25.04265)
)

# Fetch and simplify map data for each area
map_data_list <- lapply(bbox_list, function(bbox) {
  opq(bbox = bbox, timeout = 60) %>%
    add_osm_feature(key = 'highway') %>%
    osmdata_sf()
})

simplify_sf <- function(osmdata) {
  osmdata$osm_lines <- st_simplify(osmdata$osm_lines, preserveTopology = TRUE, dTolerance = 1)
  return(osmdata)
}

map_data_list <- lapply(map_data_list, simplify_sf)

# Sample counts for each area
area_counts <- Legislative_Yuan_Movement %>%
  count(area)

# Prepare base map
Legislative_Yuan_map <- 
  opq(bbox = c(121.516, 25.040, 121.525, 25.047), timeout = 60) %>%
  add_osm_feature(key = 'highway') %>%
  osmdata_sf()


Legislative_Yuan_map$osm_lines <- st_simplify(Legislative_Yuan_map$osm_lines, preserveTopology = TRUE, dTolerance = 1)

# Coordinates for text labels (approximated for each area)
label_coords <- tibble(
  area = 1:4,
  lon = c(121.520, 121.520, 121.519, 121.519),
  lat = c(25.042, 25.044, 25.043, 25.041)
)

# Merge area_counts with label coordinates
area_counts <- left_join(area_counts, label_coords, by = "area")

# Plot map with area sample counts
p <- ggplot() +
  geom_sf(data = Legislative_Yuan_map$osm_lines, color = "gray") +
  geom_sf(data = map_data_list$jinan_rd$osm_lines, color = "red") +
  geom_sf(data = map_data_list$qingdao_rd$osm_lines, color = "blue") +
  geom_sf(data = map_data_list$zhongshan_rd$osm_lines, color = "green") +
  geom_sf(data = map_data_list$jinan_church$osm_lines, color = "purple") +
  geom_point(data = area_counts, aes(x = lon, y = lat, size = n, color = factor(area)), shape = 21, fill = "white") +
  geom_text(data = area_counts, aes(x = lon, y = lat, label = n), size = 4, color = "black") +
  scale_size_continuous(range = c(3, 10)) +
  scale_color_manual(values = c("red", "blue", "green", "purple", "black"),
                     labels = c("1" = "濟南路", "2" = "青島東路", "3" = "中山南路", "4" = "濟南教會", "5" = "其他")) +
  labs(
    title = "Sample Counts of Areas",
    subtitle = "Legislative Yuan Movement",
    caption = "Data source: 臨時街頭民調小組",
    color = "Area"
  ) +
  theme_void() +
  theme(
    plot.title = element_text(size = 24, face = "bold"), # 標題字體大小和樣式
    plot.subtitle = element_text(size = 20), # 子標題字體大小
    plot.caption = element_text(size = 10), # 註腳字體大小
    legend.title = element_text(size = 16), # 圖例標題字體大小
    legend.text = element_text(size = 10), # 圖例文字字體大小
    axis.line.x = element_line(color = "black"))

p
library(svglite)
ggsave("Location_of_SampleCounts.svg", plot = p, scale = 1, width = 16, height = 9, dpi = "screen")
```

# 立院集結運動調查抽樣分佈

本次調查多數問卷題目延續2014年臺北大學社會系集結師生一起志願性動員調查的社會運動資料庫，相隔十年再次發生社會運動，一群來自各大學社會學領域的碩博士生、社會學研究者，共同籌組本次調查。抽樣設計方面，參考十年前的調查方法，考量既有人力與運動現場即時變化，及時調整抽樣調查地點，涵蓋濟南路、青島東路、中山南路與濟南教會，抽樣時間為5/21 18:00-24:00，以及5/24 11:00-24:00。針對針對青島東路、濟南路、濟南教會有固定坐位區，以五排為一區抽取，並盡可能包含流動性高的邊角座位，以及長期停留的內側座位，而中山南路因為流動性高，沒有固定座位區，改透過固定間隔抽取，以路樹、椰子樹或建築物圍牆等顯眼標誌物來劃分區域，隨機抽取一位受訪者。問卷填寫過程以受訪者自填為主，兩天累計共231位受訪者，23位受訪者拒絕訪談，完訪率90.4%（208位受訪者完成訪談）。

-   收集最多樣本的區域為主要舞台的青島東路，5/21、5/24兩天共收集92份樣本

-   其次是濟南路，兩天共收集66份樣本

-   再者是主要作為物資集結處的濟南教會，共收30份樣本

-   最後是流動性最高的中山南路，收集了13份樣本
